---
title: "Effect Size Estimation from Test Statistic in Original Studies"
output: html_document
date: '2022-11-14'
---

## Installing Relevant Packages
```{r}
install.packages('effectsize')
```
## Loading Relevant Packages

```{r}
library('effectsize')
```

## Phillips & Knobe, 2009
```{r}
t_to_d(t = 4.7, df_error = 50, paired = FALSE, ci = 0.95, alternative = "two.sided")
```

## Knobe & Fraser, 2008
```{r}
t_to_d(t = 5.5, df_error = 17, paired = FALSE, ci = 0.95, alternative = "two.sided")
```
## Cushman, Knobe, Sinnott & Armstong, 2008
```{r}
t_to_d(t = 4.3, df_error = 298, paired = FALSE, ci = 0.95, alternative = "two.sided")
```

## Young & Phillips, 2011
```{r}
# passive
t_to_d(t = 2.22, df_error = 44, paired = FALSE, ci = 0.95, alternative = "two.sided")
```

## Young & Phillips, 2011, ship
```{r}
# active
t_to_d(t = 2.22, df_error = 44, paired = FALSE, ci = 0.95, alternative = "two.sided")
```

## Young & Phillips, 2011, doctor
```{r}
# active
t_to_d(t = 3.48, df_error = 38, paired = FALSE, ci = 0.95, alternative = "two.sided")
```

## Kominsky & Phillips, 2019, battery
```{r}
# disjunctive
t_to_d(t = 5.39, df_error = 85, paired = FALSE, ci = 0.95, alternative = "two.sided")
```
## Kominsky & Phillips, 2019, bridge
```{r}
# conjunctive
t_to_d(t = -11.83, df_error = 41, paired = FALSE, ci = 0.95, alternative = "two.sided")
```
## Kominsky & Phillips, 2019, computer
```{r}
# conjunctive
t_to_d(t = -5.59, df_error = 73, paired = FALSE, ci = 0.95, alternative = "two.sided")
```

## Kominsky & Phillips, 2019, computer
```{r}
# conjunctive
t_to_d(t = -5.59, df_error = 73, paired = FALSE, ci = 0.95, alternative = "two.sided")
```

## Pettit & Knobe, 2009, decide/desire
```{r}
# decide
t_to_d(t = 2.4, df_error = 35, paired = FALSE, ci = 0.95, alternative = "two.sided")

# desire (Tannenbaum, Ditto &) Pizarro
t_to_d(t = -3.6, df_error = 52, paired = FALSE, ci = 0.95, alternative = "two.sided")
```
## Pettit & Knobe, 2009, advocate/in favour of
```{r}

F_to_d(f = 4.6, df=1, df_error = 58, paired = FALSE, ci = 0.95, alternative = "two.sided")

```

## Pettit & Knobe, 2009, opposed to
```{r}

t_to_d(t = 2.0, df_error = 54, paired = FALSE, ci = 0.95, alternative = "two.sided")

```

## Pettit & Knobe, 2009, intended to
```{r}

t_to_d(t = 2.5, df_error = 35, paired = FALSE, ci = 0.95, alternative = "two.sided")

```

## Knobe & Szabo, captain
```{r}

t_to_d(t = 7.9, df_error = 40, paired = FALSE, ci = 0.95, alternative = "two.sided")

```

## Knobe & Szabo, pen
```{r}

F_to_d(f = 43.6, df=1, df_error = 76, paired = FALSE, ci = 0.95, alternative = "two.sided")

```

## Knobe & Szabo, bull's eye
```{r}

t_to_d(t = 7.1, df_error = 50, paired = FALSE, ci = 0.95, alternative = "two.sided")

```

## Uttich & Lombrozo, 2010
```{r}

F_to_d(f = 12.83, df=1, df_error = 288, paired = FALSE, ci = 0.95, alternative = "two.sided")
```
